---
title: "Exploring the BRFSS data"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}


library(ggplot2)
library(dplyr)
library(plotly)
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `brfss2013`. Delete this note when before you submit 
your work. 

```{r load-data}
load("brfss2013.RData")
```



* * *

## Part 1: Data
### The Behavioral Risk Factor Surveillance System (BRFSS) is the nation’s premier system of health-related telephone surveys that collect state data about U.S. Established in 1984 with 15 states, BRFSS now collects data in all 50 states as well as the District of Columbia and three U.S. territories. BRFSS completes more than 400,000 adult interviews each year, making it the largest continuously conducted health survey system in the world.

### Today, all 50 states, the District of Columbia, Puerto Rico, and Guam collect data annually and American Samoa, Federated States of Micronesia, and Palau collect survey data over a limited point- in-time (usually one to three months). In this document, the term “state” is used to refer to all areas participating in BRFSS, including the District of Columbia, Guam, and the Commonwealth of Puerto Rico.

### The BRFSS objective is to collect uniform, state-specific data on preventive health practices and risk behaviors that are linked to chronic diseases, injuries, and preventable infectious diseases that affect the adult population. Factors assessed by the BRFSS in 2013 include tobacco use, HIV/AIDS knowledge and prevention, exercise, immunization, health status, healthy days — health-related quality of life, health care access, inadequate sleep, hypertension awareness, cholesterol awareness, chronic health conditions, alcohol consumption, fruits and vegetables consumption, arthritis burden, and seatbelt use. Since 2011, BRFSS conducts both landline telephone- and cellular telephone-based surveys. In conducting the BRFSS landline telephone survey, interviewers collect data from a randomly selected adult in a household. In conducting the cellular telephone version of the BRFSS questionnaire, interviewers collect data from an adult who participates by using a cellular telephone and resides in a private residence or college housing.

### Health characteristics estimated from the BRFSS pertain to the non-institutionalized adult population, aged 18 years or older, who reside in the US. In 2013, additional question sets were included as optional modules to provide a measure for several childhood health and wellness indicators, including asthma prevalence for people aged 17 years or younger.

*Dataset notes:*
### All missing values are coded NA

### Many variables, such as age, race, education, as well as variables that measure counts of events (drinks, times eating fruit, etc.) have alternate versions in the Calculated Variables section of the dataset. Review this section prior to choosing variables for analysis.

* * *

## Part 2: Research questions

**Research quesion 1:**
males vs females in income variable. 

**Research quesion 2:**

**Research quesion 3:**


* * *

## Part 3: Exploratory data analysis

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note when before you submit your work.

**Research quesion 1:**

```{r}
df <- brfss2013[,c('income2','sex')]
df$total_sex <- ifelse(df$sex == 'Male' , count(df, sex)[1,2][[1]], count(df, sex)[2,2][[1]])
dff <- df %>% 
    group_by(sex, income2 ) %>% 
    summarise(count = n(), total = mean(total_sex), percent = count / total)
dff <- na.omit(dff)
dff <- select(dff, income2, sex, percent)
x = c('< $10000', '< $15000', '< $25000', '< $35000', '<$50000', '< $75000', '>= 75000')
ggplot(data=dff, aes(x=income2, y=percent, fill=sex)) +
    geom_bar(stat="identity")+#, position=position_dodge()
  theme(axis.text.x  = element_text(angle=90, vjust=0.5, size=12))
```



**Research quesion 2:**

```{r}
df <- na.omit(brfss2013[,c("genhlth", "hlthpln1", "marital", "sleptim1")])
gp <- df %>%
    group_by(genhlth, hlthpln1) %>%
    summarise(count = n(), avg.sleptime = mean(sleptim1))
ggplot(gp, aes(x = genhlth, y = avg.sleptime, fill=hlthpln1)) + geom_bar(stat="identity")
```



**Research quesion 3:**

```{r}
brfss2013_rest_genhlth <- brfss2013 %>% filter(misrstls != "NA") %>% mutate(gen_hlth = ifelse(genhlth == "Poor", "Poor", "Good")) %>% filter(gen_hlth != "NA")
ggplot(brfss2013_rest_genhlth, aes(x = misrstls, fill = gen_hlth)) + geom_bar(position=position_dodge()) + scale_fill_discrete(name = "General Health") + xlab("Frequency of restless days") + ylab("Proportion")
```
df <- brfss2013[, c('children', 'sex', 'genhlth')]
df <- na.omit(df)
gp <- df %>%
    group_by(children, genhlth, sex) %>%
    summarise(count = n())
gp$genhelth <- NaN
gp$genhelth[gp$genhlth == 'Excellent'] <- 5
gp$genhelth[gp$genhlth == 'Very good'] <- 4
gp$genhelth[gp$genhlth == 'Good'] <- 3
gp$genhelth[gp$genhlth == 'Fair'] <- 2
gp$genhelth[gp$genhlth == 'Poor'] <- 1
ggplot(gp, aes(x = children, y = genhelth)) + geom_bar(stat="identity", position = 'dodge')#, fill=sex





df <- brfss2013[, c('educa', 'sex', 'income2')]
df <- na.omit(df)
gp <- df %>%
    group_by(educa, sex) %>%
    summarise(count = n())
ggplot(data = gp, aes(x = educa, y = count, fill = sex)) + geom_bar(stat = 'identity', position = 'dodge')+
theme(axis.text.x  = element_text(angle=90))
