---
title: "Modeling and prediction for movies"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(statsr)
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `movies`. Delete this note when before you submit 
your work. 

```{r load-data}
load("movies.Rdata")
```



* * *

## Part 1: Data

  Reasoning for generabizability:
  
    Question: Will the results be generalizable? 
    Answer: For answer this we have to check many things:
      Is data random sampled?
        Yes, It is sampled selected data, there are two possibilities,
          i- All movies are listed in  'Rotten Tomatoes' and IMDB (from where our data is sampled)
          ii- All movies are NOT listed in  'Rotten Tomatoes' and IMDB (from where our data is sampled)
        if the former, we say that this is the 'simple random sampling'.
        if the latter, we say that this is the 'stratified random sampling'.
      Is data sufficient?
        Yes, It is not large, but not small too, so we can use it for inference.
      CAUSTION: 
        There is one concern I am worried about:
          The data is for movies before 2016, and as we are in 2022, the underling distribution might have changed, if that so the result WON'T be generalizable anymore.
          
  Reasoning for causality:
  
    Since this data is came from observational study and not from experimental study; we can't use the results for causal inference.
    The 'random assignment' have not be used for collecting this data, because it is in experimental study, and our data is come from observational study.
  
* * *

## Part 2: Research question



* * *

## Part 3: Exploratory data analysis

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button above. Make sure that your code is visible in the project you submit. 
Delete this note when before you submit your work.

* * *

## Part 4: Modeling

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button above. Make sure that your code is visible in the project you submit. 
Delete this note when before you submit your work.

* * *

## Part 5: Prediction

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button above. Make sure that your code is visible in the project you submit. 
Delete this note when before you submit your work.

* * *

## Part 6: Conclusion

